\documentclass[czech,master]{diploma}
\usepackage[autostyle=true,czech=quotes]{csquotes}
\usepackage[backend=biber, style=iso-numeric, alldates=iso]{biblatex}
\usepackage{dcolumn}
\usepackage{subfig}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{tikz}
\usepackage[cpp]{diplomalst}
\usepackage{amsfonts}
\usepackage{enumerate}

\usepackage{listings}

\lstdefinelanguage{Kotlin}{
  comment=[l]{//},
  commentstyle={\color{gray}\ttfamily},
  emph={filter, first, firstOrNull, forEach, lazy, map, mapNotNull, println},
  keywords={!in, !is, abstract, actual, annotation, as, as?, break, by, catch, class, companion, const, constructor, continue, crossinline, data, delegate, do, dynamic, else, enum, expect, external, false, field, file, final, finally, for, fun, get, if, import, in, infix, init, inline, inner, interface, internal, is, lateinit, noinline, null, object, open, operator, out, override, package, param, private, property, protected, public, receiveris, reified, return, return@, sealed, set, setparam, super, suspend, tailrec, this, throw, true, try, typealias, typeof, val, var, vararg, when, where, while},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
  morestring=[s]{"""*}{*"""},
  ndkeywords={@Deprecated, @JvmField, @JvmName, @JvmOverloads, @JvmStatic, @JvmSynthetic, Array, Byte, Double, Float, Int, Integer, Iterable, Long, Runnable, Short, String, Any, Unit, Nothing},
  sensitive=true,
}

\lstdefinelanguage{Tilscript}{
  comment=[l]{--},
  commentstyle={\color{gray}\ttfamily},
  morestring=[b]",
  keywords={Defn, Import, TypeDef, Struct},
  ndkeywords={Int, Real, Time, World, List, Tuple, If, Progn, MkTuple, Cond,
    ListOf, Bool, Construction, Any1, Any2, Any3, Any4, Any5, Any6, Any7, Any8,
    Any9},
  sensitive=true,
}

\lstset{language=Tilscript}

\newcommand{\peteref}[1]{\ref{#1}\,--\,\nameref{#1}}

\usetikzlibrary{fit}

\ThesisAuthor{Bc. Filip Peterek}
\ThesisSupervisor{prof. RNDr. Marie Duží, CSc.}
\CzechThesisTitle{Implementace jazyka TIL-Script}
\EnglishThesisTitle{Implementation of the TIL-Script Language}
\SubmissionYear{2023}

\ThesisAssignmentFileName{Figures/spec.pdf}
% TODO: Doplnit
% \Acknowledgement{Děkuji Adélce za to, že mě ignoruje, a já tak mám čas psát diplomovou práci.}

\CzechAbstract{
    Cílem práce je implementovat programovací jazyk TIL-Script. Jazyk TIL-Script slouží jako
    výpočetní varianta logického kalkulu TIL, jenž umožňuje jednoduchý strojový zápis konstrukcí
    Transparentní intenzionální logiky, ale také jejich následné provedení. Práce dále řeší
    praktické problémy s interpretací jazyka TIL-Script, a to například definice pojmenovaných
    funkcí, interakce s databází, apod. Dále se práce snaží navrhnout nadmnožinu jazyka TIL-Script,
    která umožní konstrukce TILu nejen provádět, ale také analyzovat, vytvářet je, a pracovat
    s nimi.
}

\CzechKeywords{
    Transparentní intenzionální logika, TIL-Script, překladač
}

\EnglishAbstract{
    The goal of the thesis is the definition and implementation of the TIL-Script language.
    TIL-Script is a scripting language which serves the purpose of a computational variant of
    Transparent intensional logic, a logical calculus based on typed lambda calculi. TIL-Script
    allows for not just representation, but also execution of TIL constructions. This work also
    deals with practical problems of TIL-Script implementation, such as definitions of named
    functions, interaction with databases, and so on. Furthermore, this thesis attempts to define
    a superset of the TIL-Script language, which allows for not just the execution of constructions,
    but also for their creation and analysis.
}

\EnglishKeywords{
    Transparent intensional logic, TIL-Script, interpreter
}

\AddAcronym{TIL}{Transparentní intenzionální logika}
\AddAcronym{JVM}{Java Virtual Machine}
\AddAcronym{JRE}{Java Runtime Environment}
\AddAcronym{JAR}{Java Archive}
\AddAcronym{TCO}{Tail Call Optimization}
\AddAcronym{REPL}{Read-Eval-Print Loop}
\AddAcronym{CLI}{Command Line Interface}
\AddAcronym{AST}{Abstract Syntax Tree}
\AddAcronym{GCC}{GNU Compiler Collection}
\AddAcronym{GNU}{GNU is not Unix}
\AddAcronym{RCE}{Remote Code Execution}

\renewcommand\lstlistingname{Ukázka}

\begin{document}

\MakeTitlePages

\listoffigures
\clearpage

\listoftables
\clearpage

\input{Chapters/Introduction.tex}
\input{Chapters/TIL.tex}
\input{Chapters/Tilscript.tex}
\input{Chapters/Implementation.tex}
\input{Chapters/Documentation.tex}
\input{Chapters/Conclusion.tex}

% \printbibliography[title={Literatura}, heading=bibintoc]

\begin{thebibliography}{50}

\bibitem{til-duzi}
Duží, M., Materna, P.: \textit{TIL jako procedurální logika, (průvodce zvídavého čtenáře Transparentní intensionální logikou)} \\
Aleph Bratislava 2012, ISBN 978-80-89491-08-7

\bibitem{til-script}
Ciprich, N., Duží, M., Košinár, M.: \textit{TIL-Script: Functional Programming Based on
Transparent Intensional Logic} \\
In: \textit{RASLAN 2007}, Sojka, P., Horák, A., (Eds.), Masaryk University Brno, 2007, pp. 37–42.

\bibitem{antlr-src}
Parr, T.: \textit{ANTLR v4} [online, cit. 2022-06-09] \\
Dostupné z: \url{https://www.antlr.org} \\
Terence Parr

\bibitem{kotlin-src}
Kotlin: \textit{Kotlin Programming Language} [online, cit. 2022-06-09] \\
Dostupné z: \url{https://kotlinlang.org} \\
Jetbrains, s.r.o.

\bibitem{gradle-src}
Gradle: \textit{Gradle Build Tool} [online, cit. 2022-06-09] \\
Dostupné z: \url{https://gradle.org} \\
Gradle Enterprise

\bibitem{halting-problem-src}
Turing, A. M.: \textit{On Computable Numbers, With Application To Entscheidungsproblem} \\
Dostupné z: \url{https://doi.org/10.1112/plms/s2-42.1.230}\\
Proceedings of the London Mathematical Society, s2-42: 230-265.

\bibitem{lisp-src}
John McCarthy. 1960. \textit{Recursive functions of symbolic expressions and their computation by machine, Part I.}\\
Dostupné z: \url{https://doi.org/10.1145/367177.367199}
Commun. ACM 3, 4 (April 1960), 184–195.

\end{thebibliography}

\appendix
\input{Chapters/Appendix2.tex}

\end{document}
